### 2016-04-15 ch03-lrm/LPMSmooth_ML_EG_JS_JL.tex
More uniform notation in trunc

\item The work in this section is for discrete-time systems. 
Denote the $k^{\text{th}}$ discretized frequency as $\Omega_k$ = $e^{-j2{\pi}k\fs/N}$, with $f_s$ the sample frequency and $N$ the total number of sample points.

\item  Describe the parametric plant model  $G(q,\theta)$ by the nonparametric \gls{FRF} counterpart  $G(\Omega_k)$  at the $k^{\text{th}}$ frequency.

\item Describe  the parametric noise model $H(q,\theta)$ (associated with the output noise source $v(t)$) by a nonparametric noise variance contribution $\sigma^2_v(\Omega_k)$ at the $k^{\text{th}}$ frequency.

@@

The rest of the section is structured as follows. 
\secref{sec:nparam:trunc:theoryLPMandWindowing} covers the theory on the \gls{LPM} and windowing for an \gls{OE} setup.
\secref{sec:nparam:trunc:smoothingFRFestimate} discusses the novel smoothing method.
Ultimately, in \secref{sec:nparam:trunc:simResults}, simulation results of the following FRF estimates and their corresponding variances are compared: (i) the smooth \gls{LPM} estimate $\hat{G}_{\trunc}(\Omega_k)$, (ii) the \gls{LPM} estimate $\hat{G}_{\LPM}(\Omega_k)$.

These FRF estimates are also compared with the true \gls{LTI} system ${G}_0(\Omega_k)$.
Discussion of the simulation results is then followed by a conclusion in \secref{sec:nparam:trunc:conclusion}.

@@

Using convolution, the noiseless output signal in \figref{lpmtdrep} is $y_0(t) = g_0(t)*u_0(t)$, where the signals are sampled at $t = 0, 1, 2,...,N-1$ and the excitation signal $u_0(t)$ is random noise. 
As shown in \citet{Pintelon2012} and \citet{Pintelon1997ARB} the \gls{DFT} spectra of the sampled signals at the frequency $\Omega_k$ are related as follows:
\begin{equation}\label{eq:nparam:trunc:LPM:leakage}
Y_0(k)=G_0(\Omega_k)U_0(k)+T_G(\Omega_k)
\end{equation}
where $U_0(k)$ is the \gls{DFT} spectrum of the random noise excitation,  $G_0(\Omega_k)$ is the transfer function and $T_G(\Omega_k)$ is the transients leakage term.
In this section, the \gls{DFT} of a signal $x(t)$ is defined explicitly as~\citep{Oppenheim1983}

\begin{equation}\label{eq:defDFT}
X(\Omega_k) = \frac{1}{\sqrt{N}}\sum_{t=0}^{N-1}x(t)e^{-\frac{j2\pi kt}{N}}
\end{equation}

@@

% The \gls{DFT} spectra at the output of the \gls{SISO} system in \figref{lpmtdrep} are derived from equations \eqref{eq:nparam:trunc:LPM:TD} and \eqref{eq:nparam:trunc:LPM:leakage}, \emph{viz}:
% \begin{equation}\label{lpm1spectra}
% Y(k)=G_0(\Omega_k)U_0(k)+T(\Omega_k)+V_0(k)
% \end{equation}
% where $V_0(k) = H_0(\Omega_k)E(k)$ is a noise term, and $T(\Omega_k)$ is the leakage term. The latter is the sum of the system and the noise leakage terms, i.e. $T(\Omega_k) = T_G(\Omega_k) + T_H(\Omega_k)$.

% The smooth characteristics of $G_0(\Omega_k)$ and $T(\Omega_k)$ allow for the use of the Taylor series representations at the frequency lines $k+r$ in a frequency domain window of width $2n+1$, with a remainder $\bigO{\left(\frac{r}{N}\right)^{R+1}}$ of the first order Taylor series expansion \citep{Schoukens2009LPM}, \emph{viz}:
% \begin{align}\label{lpmGTaylorS}
% G_0(\Omega_{k+r})&=G_0(\Omega_k)+\sum_{p=1}^{R}g_p(k)r^p+
% \bigO{\left(\frac{r}{N}\right)^{R+1}},
% \\
% \label{lpmTTaylorS}
% T(\Omega_{k+r})&=T(\Omega_k)+\sum_{p=1}^{R}t_p(k)r^p+N^{-1/2}
% \bigO{  \left(\frac{r}{N}\right)^{R+1}  }
% ,
% \\
% \text{where}&\ r\in\mathbb{W}_n,\quad \mathbb{W}_n = \{-n,-n+1,\dots,n\}
% \end{align}

@@

% Neglecting the remainder, the Taylor series approximation of \eqref{lpm1spectra} can be written in a matrix vector form, \emph{viz}:
% \begin{equation}\label{lpmGTMatrix}
% Y(k+r)\approx{K(k, r)\theta(k)+V_0(k+r)}
% \end{equation}
% where $\theta(k)\in\mathbb{C}^{2R+2}$ is the column vector of the  parameters ($G_0(\Omega_k)$, $T(\Omega_k)$, $g_p$, $t_p$, and $p = 1, 2, ...., R$) and $K(k, r)$ is the row vector of their respective coefficients:
% \begin{align}
% K(k,r) = &\left[
% \begin{matrix}
% U_0(k+r) & U_0(k+r)r & \dots
% \end{matrix}
% \right.
% \\
% &\quad\left.\begin{matrix}U_0(k+r)r^R & 1& r&\dots&r^R\end{matrix}\right]\nonumber
% \end{align}

@@

% When substituted into equations \eqref{lpmGTaylorS} and \eqref{lpmGTMatrix},  these yield the following quadratic local polynomials of $G_0$ and $T$ around a central frequency $\Omega_{k}$:
% \begin{align}
% G_0(\Omega_{k+r})
%   &\approx 
%   G_0(\Omega_k)+g_1r+g_2r^2
%   \label{eq:lpm:expansionG:quadratic}
% \\
%   T(\Omega_{k+r})
%     &\approx 
%     T(\Omega_k)+t_1r+t_2r^2
%     \label{eq:lpm:expansionT:quadratic}
% \end{align}
% with ($r\in\mathbb{W}_3$) and the vector of parameters:
% \begin{equation}\label{lpmThetaEst}
% \theta^{\TT}(k)=\left[G_0(\Omega_k) \ g_1 \ g_2\  T_G(k)\  t_1 \ t_2\right]
% \end{equation}
% The \gls{LPM} estimate of the \gls{FRF} is the first element of the estimate $\hat\theta(k)$, obtained from \eqref{eq:LSsolutionLPM}, \emph{viz}:
% \begin{equation}
% \hat{G}_{\LPM}(\Omega_k) = \hat\theta_1(k)
% \end{equation}

The estimation of $\hat{G}_{\LPM}(\Omega_k)$ at a single frequency $\Omega_k = 0.586\unit{Hz}$ is illustrated in \figref{LPM_Schematic_EG}.% centered at $k$, where $r = 0$.
\begin{figure}[htb] %  figure placement: here, top, bottom, or page
   \centering
   \setlength{\figurewidth}{0.8\columnwidth}
   \setlength{\figureheight}{0.68\figurewidth}

   \input{\thisDir/figs/LPMfig.tikz}
   \caption[Illustration of the LPM.]{Illustration of the \gls{LPM}. Top figures: input spectrum (left) and output spectrum (right). 
   A small band is selected (gray area), in which $\hat G_{\LPM}(\Omega_{k+r})$ is estimated (black thick line, bottom figure) as a local polynomial. Only its central value $\hat G_{\LPM}(\Omega_k)$ (white circle) is retained. This procedure is repeated for all frequencies $\Omega_k$.}
   \label{LPM_Schematic_EG}
\end{figure}
This procedure is repeated at each central frequency $\Omega_k$ for  $k\in \Set{1,\dots,N/2}$ (i.e. the entire frequency band, including Nyquist, but excluding \gls{DC}, and regularizing at the boundaries). This completes the \gls{LPM}, yielding an intrinsic averaging of the spectra of the estimated \gls{FRF}, $\hat{G}_{\LPM}(\Omega_k)$.

\section{Smoothing the \gls{FRF} estimate}
\label{sec:nparam:trunc:smoothingFRFestimate}
The method for smoothing (improving) the \gls{LPM} estimate of the frequency response function  is presented in this section together with pertinent assumptions. 
After obtaining the \gls{LPM} estimate of the \gls{FRF} (denoted as $\hat{G}_{{\LPM}}(\Omega_k)$) from \secref{sec:nparam:trunc:LPMFRFest}, the smoothing method is decomposed into the following procedures, which will be elaborated on later:
\begin{enumerate}
\item The impulse response $\hat g_{\LPM}(t)$  is computed from the \gls{IDFT} of $\hat{G}_{{\LPM}}(\Omega_k)$.

@@

\begin{assumption}
The estimate $\hat G_{\LPM}(\Omega_k)$ is available at all frequencies $\Omega_k$ for $k\in\{1,2,\dots,N/2\}$.
\end{assumption}

@@

The estimated impulse response function  $\hat g_{{\LPM}\setminus \mathrm{DC
}}(t)$ is obtained explicitly via the \gls{IDFT} of the \gls{LPM}-estimate $\hat G_{\LPM}(\Omega_k)$ of the \gls{FRF} in accordance with equation \eqref{eq:defDFT}, \emph{viz}:

\begin{align}\label{eq:impRespiDFT}
\hat g_{{\LPM}\setminus \mathrm{DC
}}(t) &= \frac{1}{\sqrt{N}}\sum_{k=1}^{N-1}\hat G_{\LPM}(\Omega_k)e^{\frac{j2\pi kt}{N}}
\end{align}
where the estimated \gls{FRF} in the frequency band between  the Nyquist and the sample frequencies is obtained as follows:

\begin{align}
\hat G_{\LPM}(\Omega_{N-k}) = \overline{\hat G_{\LPM}(\Omega_k)},\ \text{for}\ k=1,\dots,N/2
\end{align}
(with $\conj{\hat G_{\LPM}}$ the complex conjugate of $\hat G_{\LPM}$) to ensure $\hat g_{\LPM}(t)$ to be real.

>>>>

\item The work in this section is for discrete-time systems. 
Denote the $k^{\text{th}}$ discretized frequency as $\omega_k$ = $e^{-j2{\pi}k\fs/N}$, with $f_s$ the sample frequency and $N$ the total number of sample points.

\item  Describe the parametric plant model  $G(q,\theta)$ by the nonparametric \gls{FRF} counterpart  $G(\omega_k)$  at the $k^{\text{th}}$ frequency.

\item Describe  the parametric noise model $H(q,\theta)$ (associated with the output noise source $v(t)$) by a nonparametric noise variance contribution $\sigma^2_v(\omega_k)$ at the $k^{\text{th}}$ frequency.

@@

The rest of the section is structured as follows. 
\secref{sec:nparam:trunc:theoryLPMandWindowing} covers the theory on the \gls{LPM} and windowing for an \gls{OE} setup.
\secref{sec:nparam:trunc:smoothingFRFestimate} discusses the novel smoothing method.
Ultimately, in \secref{sec:nparam:trunc:simResults}, simulation results of the following FRF estimates and their corresponding variances are compared: (i) the smooth \gls{LPM} estimate $\hat{G}_{\trunc}(\omega_k)$, (ii) the \gls{LPM} estimate $\hat{G}_{\LPM}(\omega_k)$.

These FRF estimates are also compared with the true \gls{LTI} system ${G}_0(\omega_k)$.
Discussion of the simulation results is then followed by a conclusion in \secref{sec:nparam:trunc:conclusion}.

@@

Using convolution, the noiseless output signal in \figref{lpmtdrep} is $y_0(t) = g_0(t)*u_0(t)$, where the signals are sampled at $t = 0, 1, 2,...,N-1$ and the excitation signal $u_0(t)$ is random noise. 
As shown in \citet{Pintelon2012} and \citet{Pintelon1997ARB} the \gls{DFT} spectra of the sampled signals at the frequency $\omega_k$ are related as follows:
\begin{equation}\label{eq:nparam:trunc:LPM:leakage}
Y_0(k)=G_0(\omega_k)U_0(k)+T_G(\omega_k)
\end{equation}
where $U_0(k)$ is the \gls{DFT} spectrum of the random noise excitation,  $G_0(\omega_k)$ is the transfer function and $T_G(\omega_k)$ is the transients leakage term.
In this section, the \gls{DFT} of a signal $x(t)$ is defined explicitly as~\citep{Oppenheim1983}

\begin{equation}\label{eq:defDFT}
X(\omega_k) = \frac{1}{\sqrt{N}}\sum_{t=0}^{N-1}x(t)e^{-\frac{j2\pi kt}{N}}
\end{equation}

@@

% The \gls{DFT} spectra at the output of the \gls{SISO} system in \figref{lpmtdrep} are derived from equations \eqref{eq:nparam:trunc:LPM:TD} and \eqref{eq:nparam:trunc:LPM:leakage}, \emph{viz}:
% \begin{equation}\label{lpm1spectra}
% Y(k)=G_0(\omega_k)U_0(k)+T(\omega_k)+V_0(k)
% \end{equation}
% where $V_0(k) = H_0(\omega_k)E(k)$ is a noise term, and $T(\omega_k)$ is the leakage term. The latter is the sum of the system and the noise leakage terms, i.e. $T(\omega_k) = T_G(\omega_k) + T_H(\omega_k)$.

% The smooth characteristics of $G_0(\omega_k)$ and $T(\omega_k)$ allow for the use of the Taylor series representations at the frequency lines $k+r$ in a frequency domain window of width $2n+1$, with a remainder $\bigO{\left(\frac{r}{N}\right)^{R+1}}$ of the first order Taylor series expansion \citep{Schoukens2009LPM}, \emph{viz}:
% \begin{align}\label{lpmGTaylorS}
% G_0(\Omega_{k+r})&=G_0(\omega_k)+\sum_{p=1}^{R}g_p(k)r^p+
% \bigO{\left(\frac{r}{N}\right)^{R+1}},
% \\
% \label{lpmTTaylorS}
% T(\Omega_{k+r})&=T(\omega_k)+\sum_{p=1}^{R}t_p(k)r^p+N^{-1/2}
% \bigO{  \left(\frac{r}{N}\right)^{R+1}  }
% ,
% \\
% \text{where}&\ r\in\mathbb{W}_n,\quad \mathbb{W}_n = \{-n,-n+1,\dots,n\}
% \end{align}

@@

% Neglecting the remainder, the Taylor series approximation of \eqref{lpm1spectra} can be written in a matrix vector form, \emph{viz}:
% \begin{equation}\label{lpmGTMatrix}
% Y(k+r)\approx{K(k, r)\theta(k)+V_0(k+r)}
% \end{equation}
% where $\theta(k)\in\mathbb{C}^{2R+2}$ is the column vector of the  parameters ($G_0(\omega_k)$, $T(\omega_k)$, $g_p$, $t_p$, and $p = 1, 2, ...., R$) and $K(k, r)$ is the row vector of their respective coefficients:
% \begin{align}
% K(k,r) = &\left[
% \begin{matrix}
% U_0(k+r) & U_0(k+r)r & \dots
% \end{matrix}
% \right.
% \\
% &\quad\left.\begin{matrix}U_0(k+r)r^R & 1& r&\dots&r^R\end{matrix}\right]\nonumber
% \end{align}

@@

% When substituted into equations \eqref{lpmGTaylorS} and \eqref{lpmGTMatrix},  these yield the following quadratic local polynomials of $G_0$ and $T$ around a central frequency $\Omega_{k}$:
% \begin{align}
% G_0(\Omega_{k+r})
%   &\approx 
%   G_0(\omega_k)+g_1r+g_2r^2
%   \label{eq:lpm:expansionG:quadratic}
% \\
%   T(\Omega_{k+r})
%     &\approx 
%     T(\omega_k)+t_1r+t_2r^2
%     \label{eq:lpm:expansionT:quadratic}
% \end{align}
% with ($r\in\mathbb{W}_3$) and the vector of parameters:
% \begin{equation}\label{lpmThetaEst}
% \theta^{\TT}(k)=\left[G_0(\omega_k) \ g_1 \ g_2\  T_G(k)\  t_1 \ t_2\right]
% \end{equation}
% The \gls{LPM} estimate of the \gls{FRF} is the first element of the estimate $\hat\theta(k)$, obtained from \eqref{eq:LSsolutionLPM}, \emph{viz}:
% \begin{equation}
% \hat{G}_{\LPM}(\omega_k) = \hat\theta_1(k)
% \end{equation}

The estimation of $\hat{G}_{\LPM}(\omega_k)$ at a single frequency $\omega_k = 0.586\unit{Hz}$ is illustrated in \figref{LPM_Schematic_EG}.% centered at $k$, where $r = 0$.
\begin{figure}[htb] %  figure placement: here, top, bottom, or page
   \centering
   \setlength{\figurewidth}{0.8\columnwidth}
   \setlength{\figureheight}{0.68\figurewidth}

   \input{\thisDir/figs/LPMfig.tikz}
   \caption[Illustration of the LPM.]{Illustration of the \gls{LPM}. Top figures: input spectrum (left) and output spectrum (right). 
   A small band is selected (gray area), in which $\hat G_{\LPM}(\Omega_{k+r})$ is estimated (black thick line, bottom figure) as a local polynomial. Only its central value $\hat G_{\LPM}(\omega_k)$ (white circle) is retained. This procedure is repeated for all frequencies $\omega_k$.}
   \label{LPM_Schematic_EG}
\end{figure}
This procedure is repeated at each central frequency $\omega_k$ for  $k\in \Set{1,\dots,N/2}$ (i.e. the entire frequency band, including Nyquist, but excluding \gls{DC}, and regularizing at the boundaries). This completes the \gls{LPM}, yielding an intrinsic averaging of the spectra of the estimated \gls{FRF}, $\hat{G}_{\LPM}(\omega_k)$.

\section{Smoothing the \gls{FRF} estimate}
\label{sec:nparam:trunc:smoothingFRFestimate}
The method for smoothing (improving) the \gls{LPM} estimate of the frequency response function  is presented in this section together with pertinent assumptions. 
After obtaining the \gls{LPM} estimate of the \gls{FRF} (denoted as $\hat{G}_{{\LPM}}(\omega_k)$) from \secref{sec:nparam:trunc:LPMFRFest}, the smoothing method is decomposed into the following procedures, which will be elaborated on later:
\begin{enumerate}
\item The impulse response $\hat g_{\LPM}(t)$  is computed from the \gls{IDFT} of $\hat{G}_{{\LPM}}(\omega_k)$.

@@

\begin{assumption}
The estimate $\hat G_{\LPM}(\omega_k)$ is available at all frequencies $\omega_k$ for $k\in\{1,2,\dots,N/2\}$.
\end{assumption}

@@

The estimated impulse response function  $\hat g_{{\LPM}\setminus \mathrm{DC
}}(t)$ is obtained explicitly via the \gls{IDFT} of the \gls{LPM}-estimate $\hat G_{\LPM}(\omega_k)$ of the \gls{FRF} in accordance with equation \eqref{eq:defDFT}, \emph{viz}:

\begin{align}\label{eq:impRespiDFT}
\hat g_{{\LPM}\setminus \mathrm{DC
}}(t) &= \frac{1}{\sqrt{N}}\sum_{k=1}^{N-1}\hat G_{\LPM}(\omega_k)e^{\frac{j2\pi kt}{N}}
\end{align}
where the estimated \gls{FRF} in the frequency band between  the Nyquist and the sample frequencies is obtained as follows:

\begin{align}
\hat G_{\LPM}(\Omega_{N-k}) = \overline{\hat G_{\LPM}(\omega_k)},\ \text{for}\ k=1,\dots,N/2
\end{align}
(with $\conj{\hat G_{\LPM}}$ the complex conjugate of $\hat G_{\LPM}$) to ensure $\hat g_{\LPM}(t)$ to be real.
